SVG: The Paper

### 2022-05-09 Analysis/index.Rmd
saving init sel hex figure
initial sel model

plt_all + plt_med

@@

create_post_plot("x") + create_post_plot("y")
```

>>>>

plt_all + plt_med 
ggsave("../Figures/init_sel_hex_plot.pdf", width = 8, height = 4)

@@

am %>% select(-sd) %>% 
  pivot_wider(names_from = "dim", values_from = "mean") %>%
  ggplot(aes(x, y)) + 
  geom_point(alpha = 0.5) + 
  geom_line(data = tibble(), aes(x = c(0, 1), y = c(0, 0)), color = "grey") +
  geom_line(data = tibble(), aes(x = c(0, 1), y = c(1, 1)), color = "grey") +
  geom_line(data = tibble(), aes(x = c(0, 0), y = c(0, 1)), color = "grey") +
  geom_line(data = tibble(), aes(x = c(1, 1), y = c(0, 1)), color = "grey") -> plt_m

create_post_plot("x") + create_post_plot("y") + plt_m
ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3)
```
